\documentclass[12pt]{article}

\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage[a4paper, margin=1.2cm, bottom=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{mdwlist}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{color, soul}

\graphicspath{{./_img/}}
\setlength{\parindent}{0cm}

\title{\textbf{Combinatorics}}
\date{}

\begin{document}

\maketitle

\begin{spacing}{1.5}

\section{An Overview}

\begin{itemize*}
	\item Sum/Product rule
	\item Permutations \& Combinations
	\item Pigeonhole principle
	\item Inclusion/exclusion principle
	\item Recurrence relations
	\item Generating functions (power series)
\end{itemize*}

\section{Product rule (dependence on other tasks)}

When operation \hl{can} be broken down into 2 or more tasks. Number of ways to perform a task depend on how previous tasks are performed. Number of was to perform each task constant regardless of actions taken in prior tasks

\underline{Example}

How to label seats with a letter and a positive integer not exceeding 100. 

$\text{ways} = 26 \times 100 = 2600$

\section{Sum rule (independent of other tasks)}

When operation \hl{cannot} be broken down into 2 or more tasks that cannot be down at the same time

\underline{Example}

How to choose 1 orange and 1 apple from a basket of 10 oranges and 20 apples. 

$\text{ways} = 10 + 20$

\section{Difference rule}

$$(\text{finiteSet}(A) \wedge (B \subset A)) \Rightarrow (|A-B| = |A|-|B|)$$

\underline{Example}

How many passwords are there if: passwords are 6 to 8 alpha-numeric characters. Where passwords must contain $\ge 1$ digit

Let $P$ be total number of passwords. $P_6, P_7, P_8$ be passwords with 6, 7 or 8 alphanumeric characters long. 

$P_i = \text{alphanumeric} - \text{all letters}$

$P_6 = 36^6 - 26^6$

$P_7 = 36^7 - 26^7$

$P_8 = 36^8 - 26^8$

$P = P_6 + P_7 + P_8$

\section{Inclusion-Exclusion principle}

$$|A \cup B| = |A| + |B| - |A \cap B|$$

$$|A \cup B \cup C| = |A| + |B| + |C| - |A \cap B| - |B \cap C| - |A \cap C| + |A \cap B \cap C|$$

\section{Permutations}

Ordered arrangement of objects. 

\underline{Example}

Permutations of "abc" $ = 3 \times 2 \times 1 = 3!$

\subsection{r-Permutations}

$$P(n, r) = \frac{n!}{(n-r)!}$$

\underline{Example}

How many permutations of "abcde" to create a string of length 3 $ = 5! / 2!$

\subsection{r-Permutation with repetetion}

$$n^r$$

How many possible stings of length 3 can I build with "abced" $ = 5^3$

\section{Combinations}

Unordered selection of elements

\subsection{r-Combinations}

$$C(n, r) = \left( \begin{array}{c} a \\ b \end{array} \right) = \frac{n!}{r!(n-r)!}$$

$$C(n,r) = C(n, n-r)$$

\subsection{r-Combination with repetition}

$$C(n+r-1, r) = C(n+r-1, n-1)$$

\section{Pigeonhole Principle}

If $k + 1$ or more objects are placed into $k$ boxes, at least 1 box contains 2 or more objects 

\section{Inclusion-Exclusion Principle}

$$|A_1 \cup A_2 \cup ... \cup A_n|  = \sum_{1 \le i \le n} |A_i| - \sum_{1 \le i < j \le n} |A_i \cap A_j| + ... + (-1)^{n+1} |A_1 \cap A_2 \cap ... \cap A_n|$$

OR

$$N(P_1' P_2' ...) = N - \sum_{i = 1}^n N(P_i)$$


\end{spacing}

\end{document}
